Probabilistic Catalogs for Crowded Stellar Fields

### 2012-10-30 paper/ms.tex
Nicer table format
Paragraph on test case 1

\begin{table}\footnotesize
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Test Case & Parameter & Value \\
\hline
1 & $N$ & 100\\
  & $h_1$ & 0.3\\
  & $h_2$ & 0.6\\
  & $\alpha_1$ & 1.1\\
  & $\alpha_2$ & 2\\
  & $\sigma$ & 0.05\\
\hline
2 & $N$ & 1000\\
  & $h_1$ & 0.3\\
  & $h_2$ & 0.6\\
  & $\alpha_1$ & 1.1\\
  & $\alpha_2$ & 2\\
  & $\sigma$ & 0.3\\
\hline
\end{tabular}
\end{center}
\caption{True parameter values used to generate the simulated data. The main
difference between the two datasets is the number of stars.
\label{tab:truth}}
\end{table}

@@

\subsection{Test Case 1}
Test Case 1 was run with the DNS algorithm.

>>>>

\begin{table}\footnotesize
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Parameter & Value (Test Case 1) & Value (Test Case 2)\\
\hline
$N$ & 100 & 1000\\
$h_1$ & 0.3 & 0.3\\
$h_2$ & 0.6 & 0.6\\
$\alpha_1$ & 1.1 & 1.1\\
$\alpha_2$ & 2 & 2\\
\hline
$\sigma$ & 0.05 & 0.3\\
$s_1$ & 0.02 & 0.02\\
$s_2$ & 0.1 & 0.1\\
$w$ & 0.5 & 0.5\\
\hline
\end{tabular}
\end{center}
\caption{True parameter values used to generate the simulated data. The main
difference between the two test cases is the number of stars and the noise level.
\label{tab:truth}}
\end{table}

@@

\subsection{Test Case 1}
Test Case 1 was run with the DNS algorithm and usable results were obtained
within about an hour on a modern desktop PC. The inferences on the parameters
$N$, $h_1$, $h_2$, $\alpha_1$, and $\alpha_2$ are shown in
Figure~\ref{fig:results1}. The number of stars is correctly inferred, and the
posterior distributions for the other parameters comfortably contain the true
input values. Note that the uncertainty in $h_2$, $\alpha_1$, and $\alpha_2$ is
quite large. This is because the broken power-law model
(Figure~\ref{fig:powerlaw}) does not change drastically in shape as the
parameters are varied. Therefore, a large number of stars would be required to
tightly constrain the parameters.
